My deepest gratitude is to my advisor, Professor François Golse, whose expertise and knowledge added considerably to my graduate experience. I am fortunate to have an advisor who gave me the freedom to explore on my own, and at the same time gave an advice whenever it was necessary.

My sincerest thanks go to Professor Kazuo Aoki and to Professor Laurent Desvillettes for accepting to read and review my thesis. I would also like to thank the members of my committee, Doctor Yann Brenier, Professor Grégoire Allaire, Professor Anne Nouri, and Professor Ning Jiang. 

I can not avoid mentioning Laurent Mazet et Frédéric Charve from  Laboratoire d'Analyse et de Mathématiques Appliquées at the University Paris XII. Their help was invaluable for the preparation of my defence presentation.

I am grateful to Inessa Matveeva from the Sobolev Institute of Mathematics in Novosibirsk, the supervisor of my bachelor and master diplomas, for guiding  my first steps in research and teaching me how to write a good mathematical text.

I owe my gratitude to all members of the Centre de Mathématiques Laurent Schwartz for the enjoyable four years I spent here. I am grateful to Michèle Lavallette, Pascale Fuseau, Marine Amier, and Carole Juppin for their efficient help with all administrative procedures I had to pass as a foreign student.

I would also like to thank my fellow Ph.D. students, especially Tatiana, Jacek, Iván, and Thomas for our interesting and stimulating discussions on various topics, for good laughs and tricky mathematical problems we shared.

Last but the least, my parents have always been a source of strength, advice, and encouragement through all endeavours I ever undertook. I would like to thank my sister for being such an artistic inspiration. And, of course, the continuous support and care of my wife Natalia helped me overcome many obstacles and setbacks.
